Dynamic Slice Backsolving

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
added arch figure, maybe a little big

@@

\chapter{Fuzzing by Example}

@@

\subsection{Microsoft SAGE}

@@

\subsection{Grey-box Evolutionary Fuzzing}

@@

\chapter{Related Work}

@@

\chapter{Techniques}

@@

\section{Dynamic Taint Analysis}

@@

\section{Symbolic Execution}

@@

\section{Mixed and Concolic Execution}

@@

\section{TODO Conversion to an Intermediate Representation}

@@

\chapter{Contribution}

>>>>

%\usepackage[latin1]{inputenc}
\usetikzlibrary{shapes,arrows}

@@

\chapter{Background and Related Work}

@@

\section{Microsoft SAGE}

@@

\section{Grey-box Evolutionary Fuzzing}

@@

@@

\section{Techniques}

@@

\subsection{Dynamic Taint Analysis}

@@

\subsection{Symbolic Execution}

@@

\subsection{Mixed and Concolic Execution}

@@

\subsection{TODO Conversion to an Intermediate Representation}

@@

\chapter{Contributions}

\section{Dynamic Slice Backsolving}

\section{Design}

Stubble architecture

% Source: http://www.texample.net/tikz/examples/simple-flow-chart/

% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=5em, text centered, rounded corners, minimum height=4em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
    minimum height=2em]

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
    \node [block] (driver) {driver};
    \node [cloud, left of=driver, node distance=3cm] (binary) {binary};
    \node [cloud, right of=driver, node distance=3cm] (test case) {test case};
    \node [block, below of=driver, node distance=4cm] (Pintool) {Pintool};

    \node [block, left of=Pintool, node distance=4cm] (input) {input/};    
    \node [block, below of=Pintool, below of=input, node distance=2cm] (output) {output/};
    \node [block, right of=output, node distance=4cm] (explored) {explored/};

    \node [decision, right of=Pintool, node distance=4cm] (decide) {More taint to explore?};
    \node [block, right of=decide, node distance=4cm] (mutate) {mutate};
    \node [block, below of=decide, node distance=4cm] (stop) {stop};

    % Draw edges
    \path [line] (driver) -- (Pintool);
    \path [line] (Pintool) -- (input);
    \path [line] (Pintool) -- (output);
    \path [line] (Pintool) -- (explored);
    \path [line] (Pintool) -- (decide);
    \path [line] (decide) -- node {yes} (mutate);
    \path [line] (mutate) |- (test case);
    \path [line] (decide) -- node {no}(stop);
    \path [line,dashed] (binary) -- (driver);
    \path [line,dashed] (test case) -- (driver);
    \path [line, dashed] (explored) -- (decide);

\end{tikzpicture}

Pintool, python specifics. Binarys, RE

MyPinToolMultiProcess, why process level instead of threads, etc.

\section{Testing}

\chapter{Old Contributions}
